Manuscript figures

### 2022-10-10 docs/manuscript_figures.Rmd
Update figures in manuscript for revision

# Make overview
xlim <- c(st_bbox(countries)[1] + 3, st_bbox(countries)[3] - 3)
ylim <- c(st_bbox(countries)[2] + 3, st_bbox(countries)[4] - 3)
overview <- ggplotGrob(ggplot(tz_bry) +
    geom_sf(fill = 'lightblue', color = 'grey') +
    geom_sf_text(aes(label = geounit), size = 4) +
    geom_sf(data = countries, fill = NA, color = 'grey') +
    geom_sf(data = study_area, fill = 'red', color = 'grey') +
    coord_sf(xlim = xlim, ylim = ylim) +
    theme_bw() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4), "cm")))

# Make the main figure
main_fg <- ggplot(ecozones) +
    geom_sf(aes(fill = Ecozone), 
            color = 'grey') +
    scale_fill_brewer(palette = 'Accent') +
    geom_sf(data = nicfi_tiles, fill = NA, 
            aes(color = "black", lty = "dotted"), 
            lwd = 0.4) +
    geom_sf(data = study_area, fill = NA, 
            aes(color = 'red', lty = 'solid')) +
    scale_color_identity(name = '',
                         breaks = c('black', 'red'),
                         labels = c('NICFI tiles', 'Study area'),
                         guide = 'legend') +
    scale_linetype_identity(name = '',
                            breaks = c('dotted', 'solid'),
                            labels = c('NICFI tiles', 'Study area'),
                            guide = 'legend') +
    annotation_custom(grob = overview, 
                      xmin = 36.5, xmax = 38.5,
                      ymin = -2.3, ymax = -0.5) +
    annotation_scale(location = 'br', text_cex = 0.8) +
    annotation_north_arrow(which_north = "true", location = 'tl',
                           height = unit(1.0, "cm"), width = unit(1.0, "cm")) +
    theme_void() + 
    theme(legend.position = "bottom",
          text = element_text(size = 13),
          plot.margin = unit(c(0.3, rep(0, 3)),"cm")) +
    guides(fill = guide_legend(nrow = 4, title.position = "top"),
           color = guide_legend(nrow = 2))

# Figure 1, combination art
# Single column figure, 1772 * 1772 at 500 dpi
ggsave(here('docs/figures/figure1_study_area.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 1772, height = 1772)
```

@@

pred_eval <- left_join(pred, lc_types, 
                       by = c('predict' = 'id')) %>% 
    dplyr::select(-predict) %>% 
    rename(predict = type) %>% 
    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
    dplyr::select(-test) %>% 
    rename(test = type_use) %>% 
    mutate(predict = factor(predict, 
                            levels = c('Cropland', 'Forest/dense tree', 
                                       'Grassland', 'Shrubland', 'Water', 
                                       'Built-up','Bareland')),
           test = factor(test,
                         levels = c('Cropland', 'Forest/dense tree', 
                                    'Grassland', 'Shrubland', 'Water', 
                                    'Built-up','Bareland')))

cf <- confusionMatrix(data = pred_eval$predict, 
                      reference = pred_eval$test)
save(cf, file = here('docs/figures/rf_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/rf_test_acc.csv'),
          row.names = F)
```

@@

# Test
sample_test <- read_sf(here('data/north/plys_holdout_check.geojson'))
pred <- rast(here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_north.tif')))
sample_test <- vect(sample_test %>% st_transform(crs = crs(pred)))
pred_eval <- terra::extract(pred, sample_test, list = T)
pred_eval <- do.call(rbind, lapply(1:length(pred_eval), function(n){
    rst_vals <- pred_eval[[n]][[1]]
    data.frame(predict = rst_vals,
               test = sample_test[n, ]$landcover)
}))

lc_types <- data.frame(id = 1:7,
                       type = c('cropland', 'forest', 'grassland',
                                'shrubland', 'water', 'built-up',
                                'bareland'))
# pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
#     dplyr::select(-test) %>% 
#     rename(test = id) %>% 
#     mutate(predict = as.factor(predict),
#            test = as.factor(test))
pred_eval <- left_join(pred_eval, lc_types, 
                       by = c('predict' = 'id')) %>% 
    dplyr::select(-predict) %>% 
    rename(predict = type) %>% 
    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
    dplyr::select(-test) %>% 
    rename(test = type_use) %>% 
    mutate(predict = factor(predict, 
                            levels = c('Cropland', 'Forest/dense tree', 
                                       'Grassland', 'Shrubland', 'Water', 
                                       'Built-up','Bareland')),
           test = factor(test,
                         levels = c('Cropland', 'Forest/dense tree', 
                                    'Grassland', 'Shrubland', 'Water', 
                                    'Built-up','Bareland')))

cf <- confusionMatrix(data=pred_eval$predict, reference = pred_eval$test)
save(cf, file = here('docs/figures/test_conf.rda'))

@@

```{r}
# Class proportion, class 1 - 7
cls_prop <- cls_freq %>% 
    slice(1:7) %>% 
    mutate(proportion = ratio / sum(.$ratio)) %>% 
    select(landcover, proportion)

@@

# Calculate the area of the whole image
pred_area <- rast(pred_path)
cell_num <- freq(pred_area)
whole_area <- sum(cell_num[1:7, 3]) * 
    (res(pred_area)[1] / 1000) * 
    (res(pred_area)[2] / 1000)
class_area <- cf_ratio["Pj", ] * whole_area
class_area[, '8'] <- cell_num[[8, 3]] * 
    (res(pred_area)[1] / 1000) * 
    (res(pred_area)[2] / 1000)

@@

adjust_stats_area <- data.frame(
    area = unlist(class_area),
    confidence_interval = c(adjust_class_err, NA),
    proportion = cls_freq[, 2])
save(adjust_stats_area, file = 'docs/figures/adjust_stats_area.rda')

@@

r_df <- data.frame(x = 1:8, 
                   y = 1:8,
                   rst = as.factor(1:8))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    geom_polygon(data = r_df, fill = NA, color = "black", size = 1,
            aes(x = x, y = y, lty = 'solid')) +
    scale_fill_manual('',
                      values = color_tb$color, 
                      breaks = 1:8,
                      labels = color_tb$type) +
    scale_linetype_identity(name = '',
                            breaks = c('solid'),
                            labels = c('Examples in Figure 7'),
                            guide = 'legend') +
    theme_void() +
    theme(legend.position = 'right',
          text = element_text(size = 14),
          legend.text = element_text(size = 14),
          plot.margin = unit(rep(-1, 4),"cm"))+
    guides(fill = guide_legend(ncol = 4))
legend_lc <- get_legend(legend_lc)
f1 <- ggarrange(pred_final, legend_lc, NA, 
                nrow = 3, heights = c(5, 1, 0.5))

# # Get pie chart for class frequency
# cls_freq <- rast(pred_path)
# cls_freq <- freq(cls_freq) %>% 
#     data.frame() %>% 
#     mutate(landcover = value,
#            ratio = count / sum(.$count)) %>% 
#     select(landcover, ratio)
# save(cls_freq, file = 'docs/figures/cls_freq.rda')
# 
# 
# cls_freq <- cls_freq %>% arrange(landcover)
# cols <- color_tb$color
# lab <- paste0(round(cls_freq$ratio/sum(cls_freq$ratio) * 100, 1), "%")
# 
# # Barplot
# cls_freq <- cls_freq %>% 
#     mutate(landcover = factor(landcover, 
#                               levels = cls_freq %>% 
#                                arrange(desc(ratio)) %>% 
#                                pull(landcover)),
#         label_ypos = 0.9 * ratio)
# barplot <- ggplot(data=cls_freq, aes(x=landcover, y=ratio)) +
#     geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
#     geom_text(aes(y=label_ypos, label=lab), angle = 90,
#               color="black", size = 4)+
#     scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
#     theme_void() +
#     theme(legend.position = "none",
#           plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))

# Barplot
cls_freq <- data.frame(area = unlist(class_area) / whole_area * 100,
                       err = c(adjust_class_err / whole_area * 100, 0),
                       landcover = color_tb$id) %>% 
    mutate(err_adjust_prop = glue(
        paste0('{format(round(area, digits = 1), nsmall = 1)}',
               '\u00B1{format(round(err, digits = 1), nsmall = 1)}',
               '%'))) %>% 
    arrange(-area) %>% 
    mutate(label_ypos = c(0.75, 0.75, 0.52, 2.9, 3, 3.8, 5.2, 12)* area)
cls_freq <- cls_freq %>% 
    mutate(landcover = factor(landcover, 
                              levels = cls_freq %>% 
                                  arrange(desc(area)) %>% 
                                  pull(landcover)))
barplot <- ggplot(data=cls_freq, aes(x=landcover, y = area)) +
    geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
    geom_errorbar(aes(ymin = area - err, ymax = area + err), 
                  width = .4, color = "black", size = 0.6,
                  position = position_dodge(.9)) +
    geom_text(aes(y=label_ypos, label=err_adjust_prop), angle = 90,
              color="black", size = 4)+
    scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
    theme_void() +
    theme(legend.position = "none",
          plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))

# Table
adjust_stats_area <- adjust_stats_area %>% 
    mutate(Landcover = color_tb$type) %>% 
    arrange(desc(area)) %>% 
    mutate(`Error-adjusted area` = glue(
        paste0('{format(round(area, digits = 1), nsmall = 1)}',
               '\u00B1{format(round(confidence_interval, digits = 1), nsmall = 1)}',
               ' km\u00B2'))) %>% 
    select(Landcover, `Error-adjusted area`)
adjust_stats_area[8, 2] <- '1435.7 km\u00B2*'

@@

# Figure 7, combination art
# 1.5 column figure , 2756 * 1700 at 500 dpi
ggsave(here('docs/figures/figure7_final_map.tiff'),
       pred_final_plt, bg = "white", 
       width = 2756, height = 1700, 
       units = "px")
```

@@

# Figure 8, combination art
# 2 column figure (6.2 in) , 3150 * 2600 at 500 dpi
ggsave(here('docs/figures/figure8_compare_examples.tiff'),
       examples, bg = "white", 
       width = 3150, height = 2600, 
       units = "px")
```

@@

```{r}
cm <- pred_eval %>% 
    conf_mat(truth = test, 
             estimate = predict)
cm_figure <- autoplot(cm, type = 'heatmap') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggsave(here('docs/figures/rf_cm_heatmap.png'),
       cm_figure,
       width = 5, height = 3.5, dpi = 300)
```

### Confusion matrix heatmap for U-Net
```{r}
cm <- pred_eval %>% 
    conf_mat(truth = test, 
             estimate = predict)
cm_figure <- autoplot(cm, type = 'heatmap') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggsave(here('docs/figures/unet_cm_heatmap.png'),
       cm_figure,
       width = 5, height = 3.5, dpi = 300)
```

@@

pred_path <- here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_confidence_north_withwl.tif'))
pred <- read_stars(pred_path)
wetlands <- read_stars(file.path('results/dl/prediction',
                                 'unet_k15_only_clr_200epc',
                                 'wetland_add.tif'))
pred[wetlands == 1] <- NA
conf_fig <- tm_shape(pred) +
    tm_raster("landcover_confidence_north_withwl.tif", 
              title = "Confidence",
              style = 'cont',
              palette = rev(
                  get_brewer_pal('Greys', 
                                 plot = F, 
                                 contrast=c(.25, 1)))) +
    tm_layout(frame = F,
              legend.position = c(0.8, 0.7))
tmap_save(conf_fig, 
          here('docs/figures/conf_figure.png'), 
          width = 4, height = 4, units = 'in',
          dpi = 300)
```

>>>>

# Make overview
xlim <- c(st_bbox(countries)[1] + 3, st_bbox(countries)[3] - 3)
ylim <- c(st_bbox(countries)[2] + 3, st_bbox(countries)[4] - 3)
overview <- ggplotGrob(ggplot(tz_bry) +
    geom_sf(fill = 'lightblue', color = 'grey') +
    geom_sf_text(aes(label = geounit), size = 5) +
    geom_sf(data = countries, fill = NA, color = 'grey') +
    geom_sf(data = study_area, fill = 'red', color = 'grey') +
    coord_sf(xlim = xlim, ylim = ylim) +
    theme_bw() +
    theme(axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid.major = element_blank(),
          panel.background = element_rect(fill = "gray100",
                                          color = "black"),
          plot.margin = unit(rep(0, 4), "cm"),
          plot.background = element_rect(fill = "white")))

# Make the main figure
main_fg <- ggplot(ecozones) +
    geom_sf(aes(fill = Ecozone), 
            color = 'grey') +
    scale_fill_brewer(palette = 'Accent') +
    geom_sf(data = nicfi_tiles, fill = NA, 
            aes(color = "black", lty = "dotted"), 
            lwd = 0.4) +
    geom_sf(data = study_area, fill = NA, 
            aes(color = 'red', lty = 'solid')) +
    scale_color_identity(name = '',
                         breaks = c('black', 'red'),
                         labels = c('NICFI tiles', 'Study area'),
                         guide = 'legend') +
    scale_linetype_identity(name = '',
                            breaks = c('dotted', 'solid'),
                            labels = c('NICFI tiles', 'Study area'),
                            guide = 'legend') +
    annotation_custom(grob = overview, 
                      xmin = 36.64, xmax = 38.54,
                      ymin = -2.3, ymax = -0.62) +
    annotation_scale(location = 'br', text_cex = 0.8) +
    annotation_north_arrow(which_north = "true", location = 'tl',
                           height = unit(1.0, "cm"), width = unit(1.0, "cm")) +
    theme_linedraw() + 
    theme(legend.position = "bottom",
          text = element_text(size = 18),
          legend.spacing = unit(-1, "cm"),
          plot.margin = unit(c(0.3, rep(0, 3)),"cm")) +
    guides(fill = guide_legend(ncol = 1, title.position = "top", order = 1),
           color = guide_legend(nrow = 2, order = 2),
           linetype = guide_legend(nrow = 2, order = 2))

# Figure 1, combination art
# Single column figure, 1772 * 1772 at 500 dpi
ggsave(here('docs/figures/figure1_study_area.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 1772, height = 2200)
```

@@

pred_eval_rf <- left_join(pred, lc_types, 
                       by = c('predict' = 'id')) %>% 
    dplyr::select(-predict) %>% 
    rename(predict = type) %>% 
    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
    dplyr::select(-test) %>% 
    rename(test = type_use) %>% 
    mutate(predict = factor(predict, 
                            levels = c('Cropland', 'Forest/dense tree', 
                                       'Grassland', 'Shrubland', 'Water', 
                                       'Built-up','Bareland')),
           test = factor(test,
                         levels = c('Cropland', 'Forest/dense tree', 
                                    'Grassland', 'Shrubland', 'Water', 
                                    'Built-up','Bareland')))

cf_rf <- confusionMatrix(data = pred_eval_rf$predict, 
                      reference = pred_eval_rf$test)

save(pred_eval_rf, file = here('docs/figures/rf_test_eval.rda'))
save(cf_rf, file = here('docs/figures/rf_test_conf.rda'))

acc_test_rf <- cf_rf$byClass
write.csv(acc_test_rf, here('docs/figures/rf_test_acc.csv'),
          row.names = F)
```

@@

# Test
sample_test <- read_sf(here('data/north/plys_holdout_check.geojson'))
pred <- rast(here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_north.tif')))
sample_test <- vect(sample_test %>% st_transform(crs = crs(pred)))
pred_eval <- terra::extract(pred, sample_test)

sample_test <- read_sf(here('data/north/plys_holdout_check.geojson')) %>% 
    st_drop_geometry() %>% pull(landcover)
pred_eval <- do.call(rbind, lapply(1:nrow(pred_eval), function(n){
    rst_vals <- pred_eval[n, ]
    data.frame(predict = rst_vals$landcover_north,
               test = sample_test[rst_vals$ID])
}))

pred_eval <- left_join(pred_eval, lc_types, 
                       by = c('predict' = 'id')) %>% 
    dplyr::select(-predict) %>% 
    rename(predict = type) %>% 
    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
    dplyr::select(-test) %>% 
    rename(test = type_use) %>% 
    mutate(predict = factor(predict, 
                            levels = c('Cropland', 'Forest/dense tree', 
                                       'Grassland', 'Shrubland', 'Water', 
                                       'Built-up','Bareland')),
           test = factor(test,
                         levels = c('Cropland', 'Forest/dense tree', 
                                    'Grassland', 'Shrubland', 'Water', 
                                    'Built-up','Bareland')))

cf <- confusionMatrix(data = pred_eval$predict, reference = pred_eval$test)

save(pred_eval, file = here('docs/figures/test_eval.rda'))
save(cf, file = here('docs/figures/test_conf.rda'))

@@

```{r}
# Area adjust and projection adjust area
cls_area <- terra::zonal(cell_area, pred_area, fun = "sum", na.rm = TRUE)
cls_ratio <- cls_area %>% 
    mutate(ratio = area / sum(area))

# Class proportion, class 1 - 7
cls_prop <-  data.frame(cls_area) %>% 
    rename(landcover = landcover_north, area_orig = area) %>% 
    slice(1:7) %>% 
    mutate(proportion = area_orig / sum(.$area_orig)) %>% 
    select(landcover, proportion)

@@

# Calculate the area of the whole image
whole_area <- sum(cls_area$area[1:7]) / 1000^2
class_area <- cf_ratio["Pj", ] * whole_area
class_area[, '8'] <- cls_area$area[8] / 1000^2

@@

whole_area_add_wtl <- sum(cls_area$area) / 1000^2
adjust_stats_area <- data.frame(
    area = unlist(class_area),
    confidence_interval = c(adjust_class_err, NA),
    proportion = unlist(class_area) / whole_area_add_wtl,
    prop_interval = c(adjust_class_err / whole_area_add_wtl, NA))

save(adjust_stats_area, file = 'docs/figures/adjust_modified_stats_area.rda')

@@

r_df <- data.frame(x = 1:8, 
                   y = 1:8,
                   rst = as.factor(1:8))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    geom_polygon(data = r_df, fill = NA, color = "black", size = 1,
                 aes(x = x, y = y, lty = 'solid')) +
    scale_fill_manual('',
                      values = color_tb$color, 
                      breaks = 1:8,
                      labels = color_tb$type) +
    scale_linetype_identity(name = '',
                            breaks = c('solid'),
                            labels = c('Examples in Figure 10'),
                            guide = 'legend') +
    theme_void() +
    theme(legend.position = 'right',
          text = element_text(size = 14),
          legend.text = element_text(size = 14),
          plot.margin = unit(rep(-1, 4),"cm"))+
    guides(fill = guide_legend(ncol = 4))
legend_lc <- get_legend(legend_lc)
f1 <- ggarrange(pred_final, legend_lc, NA, 
                nrow = 3, heights = c(5, 1, 0.5))

# Barplot
cls_freq <- data.frame(area = adjust_stats_area$proportion * 100,
                       err = c(adjust_stats_area$prop_interval[1:7] * 100, 0),
                       landcover = color_tb$id) %>% 
    mutate(err_adjust_prop = glue(
        paste0('{format(round(area, digits = 1), nsmall = 1)}',
               '\u00B1{format(round(err, digits = 1), nsmall = 1)}',
               '%'))) %>% 
    arrange(-area) %>% 
    mutate(label_ypos = c(0.75, 0.75, 0.52, 2.9, 3, 3.8, 5.2, 9)* area)
cls_freq[8, 4] <- '0.6%'
cls_freq <- cls_freq %>% arrange(landcover)
cols <- color_tb$color

cls_freq <- cls_freq %>% 
    mutate(landcover = factor(landcover, 
                              levels = cls_freq %>% 
                                  arrange(desc(area)) %>% 
                                  pull(landcover)))
barplot <- ggplot(data=cls_freq, aes(x=landcover, y = area)) +
    geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
    geom_errorbar(aes(ymin = area - err, ymax = area + err), 
                  width = .4, color = "black", size = 0.6,
                  position = position_dodge(.9)) +
    geom_text(aes(y=label_ypos, label=err_adjust_prop), angle = 90,
              color="black", size = 4) +
    scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
    theme_void() +
    theme(legend.position = "none",
          plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))

# Table
adjust_stats_area <- adjust_stats_area %>% 
    mutate(Landcover = color_tb$type) %>% 
    arrange(desc(area)) %>% 
    mutate(`Error-adjusted area` = glue(
        paste0('{format(round(area, digits = 1), nsmall = 1)}',
               '\u00B1{format(round(confidence_interval, digits = 1), nsmall = 1)}',
               ' km\u00B2'))) %>% 
    select(Landcover, `Error-adjusted area`)
adjust_stats_area[8, 2] <- '1420 km\u00B2*'

@@

# Figure 9, combination art
# 1.5 column figure , 2756 * 1700 at 500 dpi
ggsave(here('docs/figures/figure9_final_map.tiff'),
       pred_final_plt, bg = "white", 
       width = 2756, height = 1700, 
       units = "px")
```

@@

# Figure 10, combination art
# 2 column figure (6.2 in) , 3150 * 2600 at 500 dpi
ggsave(here('docs/figures/figure10_compare_examples.tiff'),
       examples, bg = "white", 
       width = 3150, height = 2600, 
       units = "px")
```

@@

```{r}
cm_rf <- pred_eval_rf %>% 
    conf_mat(truth = test, 
             estimate = predict)
cm_rf_fg <- autoplot(cm_rf, type = 'heatmap', label_size = 5) +
    theme(axis.text.x = element_text(
        angle = 90, vjust = 0.5, hjust = 1,
        color = "black"),
        axis.text = element_text(color = "black"),
        text = element_text(size = 20))

# Figure 7, combination art
# Single column figure, 1772 * 1772 at 500 dpi
ggsave(here('docs/figures/sup_rf_cm_heatmap.tiff'),
       cm_rf_fg, bg = "white", units = "px", 
       width = 1772, height = 1772)
```

### Confusion matrix heatmap for U-Net
```{r}
cm <- pred_eval %>% 
    conf_mat(truth = test, 
             estimate = predict)
cm_figure <- autoplot(cm, type = 'heatmap', label_size = 5) +
    theme(axis.text.x = element_text(
        angle = 90, vjust = 0.5, hjust = 1,
        color = "black"),
        axis.text = element_text(color = "black"),
        text = element_text(size = 20))

# Figure 7, combination art
# Single column figure, 1772 * 1772 at 500 dpi
ggsave(here('docs/figures/figure7_net_cm_heatmap.tiff'),
       cm_figure, bg = "white", units = "px", 
       width = 1772, height = 1772)
```

@@

pred_path <- here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_confidence_north_withwl.tif'))
pred <- read_stars(pred_path)
wetlands <- read_stars(file.path('results/dl/prediction',
                                 'unet_k15_only_clr_200epc',
                                 'wetland_add.tif'))
pred[wetlands == 1] <- NA

conf_fig <- tm_shape(pred) +
    tm_raster("landcover_confidence_north_withwl.tif", 
              title = "Confidence\n(18 - 99)",
              style = 'cont',
              palette = rev(
                  get_brewer_pal('Greys', 
                                 plot = F, 
                                 contrast=c(.25, 1)))) +
    tm_layout(frame = FALSE,
              legend.text.size = 1.1,
              legend.title.size = 1.3,
              legend.title.fontface = "bold",
              legend.height = 1,
              legend.position = c("right", "top"),
              outer.margins = c(0, 0, 0, 0.01),
              inner.margins = rep(0, 4))
conf_fig <- tmap_grob(conf_fig)
conf_fig <- ggarrange(conf_fig)

# Figure 6, confidence map
# single column figure , 2756 * 1700 at 500 dpi
ggsave(here('docs/figures/figure8_conf_map.tiff'),
       conf_fig, bg = "white", 
       width = 1772, height = 1772,
       units = "px")
```

### Figures added for manuscript revision

```{r}
# Figures for reviewer1
## Harmonic fitting
t <- seq(0, 365, 1)
y <- sin(2 * pi * t / 365)
z <- cos(2 * pi * t / 365)
one_cycle <- data.frame(t = t, sin = y, cos = z)

y <- sin(4 * pi * t / 365)
z <- cos(4 * pi * t / 365)
two_cycle <- data.frame(t = t, sin = y, cos = z)

plot(t, z, type = "l", xlab = "time")

g1 <- ggplot(one_cycle) +
    geom_line(aes(x = t, y = sin), color = "black") +
    geom_line(aes(x = t, y = cos), color = "blue") +
    theme_bw() + xlab("Time") + ylab("Value") + ggtitle("One cycle (k = 1)")

g2 <- ggplot(two_cycle) +
    geom_line(aes(x = t, y = sin), color = "black") +
    geom_line(aes(x = t, y = cos), color = "blue") +
    theme_bw() + xlab("Time") + ylab("Value") + ggtitle("Two cycles (k = 2)")
g <- ggarrange(g1, g2, ncol = 2)

ggsave("/Users/pinot/downloads/harmonics.png", g,
       width = 8, height = 3)

## LC products dis-selected after pre-assessment
# Read the boundary
tiles <- vect(here('data/geoms/tiles_nicfi_north.geojson'))

# ESRI 10m land use/land cover
fnames <- list.files("/Volumes/elephant/landcovers/ESRI_LC_2018",
                     full.names = TRUE)
fnames <- fnames[grep("37M|36M", fnames)]
esri_lc <- do.call(merge, lapply(fnames, function(fname) {
    rast(fname) %>% project("epsg:4326")
})) %>% crop(tiles) %>% mask(tiles)

writeRaster(esri_lc, "/Volumes/elephant/landcovers/esri_lc_2018.tif",
            datatype = "INT1U")

# ESACCI
esacci <- rast(file.path("/Volumes/elephant/landcovers",
                         "ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1",
                         "ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1.0.tif")) %>% 
    crop(tiles) %>% mask(tiles)

writeRaster(esacci, "/Volumes/elephant/landcovers/esacci_2016.tif",
            datatype = "INT1U")

# Globland30
globeland <- rast(file.path("/Volumes/elephant/landcovers",
                         "globeland30",
                         "tanzania_2020LC030.tif")) %>% 
    crop(tiles) %>% mask(tiles)
writeRaster(globeland, "/Volumes/elephant/landcovers/globeland30.tif",
            datatype = "INT1U")

# Color table
color_tb <- data.frame(
    id_us = 1:8,
    id_orig = c(1, 2, 3, 4, 6, 7, 8, 5),
    id_esri_lc = c(5, 2, 11, 11, 1, 7, 8, 4),
    id_esacci = c(4, 1, 3, 2, 10, 8, 7, 5),
    id_globeland = c(10, 20, 30, 40, 60, 80, 90, 50),
    type = c("Cropland", "Forest/Dense tree", 
             "Grassland", "Shrubland", 
             "Water", 'Built-up', "Bareland", 
             'Wetland'),
    color = c('#ff7f00', '#074702', '#b2df8a',
              '#33a02c', '#3347f9', '#5a6057',
              '#fdbf6f', '#0ea591'))

library(tidyterra)
library(ggpubr)

esri_lc <- rast("/Volumes/elephant/landcovers/esri_lc_2018.tif")
esri_lc <- as.factor(esri_lc)
levels(esri_lc) <- data.frame(value = color_tb$id_esri_lc, 
                              Landcover = color_tb$type) %>% slice(-3) %>% 
    mutate(Landcover = ifelse(Landcover == 'Shrubland', 
                              "Rangeland", Landcover))
coltab(esri_lc) <- data.frame(values = color_tb$id_esri_lc[-3], 
                              cols = color_tb$color[-3])
esri_fg <- ggplot() +
    geom_spatraster(data = esri_lc, aes(fill = Landcover), na.rm = TRUE) +
    scale_fill_manual('',
                      values = color_tb$color[-3], 
                      na.value = "transparent",
                      na.translate = FALSE,
                      drop = TRUE) +
    theme_void()

esacci <- rast("/Volumes/elephant/landcovers/esacci_2016.tif")
esacci <- as.factor(esacci)
levels(esacci) <- data.frame(value = color_tb$id_esacci, 
                             Landcover = color_tb$type)
coltab(esacci) <- data.frame(values = color_tb$id_esacci, cols = color_tb$color)
esacci_fg <- ggplot() +
    geom_spatraster(data = esacci, aes(fill = Landcover)) +
    scale_fill_manual('',
                      values = color_tb$color, 
                      na.translate = F, drop = TRUE,
                      na.value = "transparent") +
    theme_void()

globeland <- rast("/Volumes/elephant/landcovers/globeland30.tif")
globeland <- as.factor(globeland)
levels(globeland) <- data.frame(value = color_tb$id_globeland, 
                             Landcover = color_tb$type)
coltab(globeland) <- data.frame(values = color_tb$id_globeland,
                             cols = color_tb$color)
globeland_fg <- ggplot() +
    geom_spatraster(data = globeland, aes(fill = Landcover)) +
    scale_fill_manual("",
                      values = color_tb$color, 
                      na.translate = F, drop = TRUE,
                      na.value = "transparent") +
    theme_void()

esaglc <- rast("data/landcovers/esaglc_rcl.tif") %>% 
    crop(tiles) %>% mask(tiles)
esaglc <- as.factor(esaglc)
levels(esaglc) <- data.frame(value = color_tb$id_orig, 
                                Landcover = color_tb$type)
coltab(esaglc) <- data.frame(values = color_tb$id_orig,
                                cols = color_tb$color)
esaglc_fg <- ggplot() +
    geom_spatraster(data = esaglc, aes(fill = Landcover)) +
    scale_fill_manual("",
                      values = color_tb$color, 
                      na.translate = F, drop = TRUE,
                      na.value = "transparent") +
    theme_void()

fromglc <- rast("data/landcovers/fromglc_rcl.tif") %>% 
    crop(tiles) %>% mask(tiles)
fromglc <- as.factor(fromglc)
levels(fromglc) <- data.frame(value = color_tb$id_orig, 
                              Landcover = color_tb$type)
coltab(fromglc) <- data.frame(values = color_tb$id_orig,
                              cols = color_tb$color)
fromglc_fg <- ggplot() +
    geom_spatraster(data = fromglc, aes(fill = Landcover)) +
    scale_fill_manual("",
                      values = color_tb$color, 
                      na.translate = F, drop = TRUE,
                      na.value = "transparent") +
    theme_void()

gfsad <- rast("data/landcovers/gfsad_rcl.tif") %>% 
    crop(tiles) %>% mask(tiles)
gfsad[gfsad == 6] <- NA
tansis <- rast("data/tansis/TZ_CP_preds_2018.tif") %>% 
    subset(7) %>% project("epsg:4326") %>% 
    crop(tiles) %>% mask(tiles) %>% 
    project(gfsad, method = "near")
gfsad[is.na(gfsad)] <- 0
tansis[is.na(tansis)] <- 0
tansis[tansis == 1] <- 3
crop_mask <- gfsad + tansis
crop_mask[crop_mask == 0] <- NA

crop_mask <- as.factor(crop_mask)
levels(crop_mask) <- data.frame(value = c(1, 3, 4), 
                             Landcover = c("Only GFSAD30", "Only TanSIS", "Overlap"))
coltab(crop_mask) <- data.frame(values = c(1, 3, 4),
                             cols = c("#c6e92b", "red", "#ff7f00"))

crop_fg <- ggplot() +
    geom_spatraster(data = crop_mask, na.rm = TRUE) +
    scale_fill_manual("",
                      values = c("#c6e92b", "red", "#ff7f00"), 
                      na.translate = F, drop = TRUE,
                      na.value = "transparent") +
    theme_void()

fg_prds <- ggarrange(esacci_fg, globeland_fg, esri_fg, 
                     esaglc_fg, fromglc_fg, crop_fg, 
                     labels = c("ESACCI S2 prototype LC (2016)",
                                "GLOBELAND30 (2010)",
                                "Esri Land Cover (2018)",
                                "CGLS_LC (2018)", "FROM-GLC (2017)",
                                "GFSAD30 + TanSIS"),
                     font.label = list(face = "plain", size = 12),
                     hjust = c(-0.1, -0.2, -0.2, -0.2, -0.2, -0.2),
                     ncol = 3, nrow = 2, common.legend = TRUE,
                     legend = "bottom")

ggsave(here('docs/figures/sup_figure_products.tiff'),
       fg_prds, bg = "white", 
       width = 8, height = 5.5, dpi = 300)

# Label editing
## Type 0: No need to do any edits (This does not mean the label is perfect).
## Type 1: Include classes that do not exit, e.g. no cropland in one tile.
### Human-part editing: Interpret the error, 
#### if the misclassfied class is clearly another class, 
#### then run the script tp directly change the class index.
#### if not, set 0 as the probability weight and run the script to 
#### recalculate the classes. Then double check the result.
## Type 2: The ratio of classes are improper.
## This case can be fixed by signing a smaller/higher weight to the probability
## and recalculate the land cover classes.
## For example, cropland is overestimated and shrubland is underestimated.
## Type 3: Some objects are missed/misclassfied in the tile. 
## This case cannot be fixed by the method proposed in type 2. 
## For example, some small pieces of farms are missed.
## Some road features are missed.
## Type 4: Too complex to fix by simple method. Tried the methods in type 1-3,
## leave it as it is, and give it a lower score.

# Examples
examples <- data.frame(id = c("1219-994_53", "1223-1014_10",
                              "1216-1016_54", "1228-997_40",
                              "1233-993_64"),
                       type = c("Type 0", "Type 2", "Type 1", 
                                "Type 3", "Type 4"))
guess_path <- "results/north/guess_labels"
refine_path <- "results/north/refine_labels"

fgs <- lapply(examples$type, function(tp){
    id <- examples %>% filter(type == tp) %>% pull(id)
    guess_lb <- rast(file.path(guess_path, 
                               sprintf("guess_%s.tif", id))) %>% 
        as.factor()
    levels(guess_lb) <- data.frame(value = color_tb$id_us, 
                              Landcover = color_tb$type)
    coltab(guess_lb) <- data.frame(values = color_tb$id_us, 
                                   cols = color_tb$color)
